### 2019-07-22 1_introduction.tex
Collapse itemize.

% The paper is organized as follows:
This paper makes the following contributions:

% FIXME: if you need more space you can collapsed the itemize:

\begin{itemize}
\item Section~\ref{sec:task-bench} describes the design of Task Bench.
\item Section~\ref{sec:implementation} details the implementation of
  Task Bench in 15 programming systems.
\item Section~\ref{sec:metg} defines the METG(50\%) metric and its
  relationship to quantities of interest to application developers.
\item Section~\ref{sec:evaluation} provides a comprehensive evaluation
  of Task Bench on up to 256 Haswell nodes of the Cori
  supercomputer~\cite{Cori}.
\end{itemize}

Section~\ref{sec:related-work} relates this work to previous efforts,
and Section~\ref{sec:conclusion} concludes.

>>>>

The paper is organized as follows: Section~\ref{sec:task-bench}
describes the design of Task Bench, Section~\ref{sec:implementation}
details the implementation of Task Bench in 15 programming systems,
Section~\ref{sec:metg} defines the METG(50\%) metric and its
relationship to quantities of interest to application developers,
Section~\ref{sec:evaluation} provides a comprehensive evaluation of
Task Bench on up to 256 Haswell nodes of the Cori
supercomputer~\cite{Cori}, Section~\ref{sec:related-work} relates this
work to previous efforts, and Section~\ref{sec:conclusion} concludes.
